Debiased Calibration for Generalized Two-Phase Sampling

### 2024-04-23 final/reports/prelim_paper.tex
Ran several basic simulations. Additional algorithms did not work.

where for $q_i = q(x_i)$ and is a function of $x_i$,
$$
\hat \beta_q = \left(\sum_{i \in A_2} 
  \frac{x_i x_i'}{\pi_{1i} q_i}\right)^{-1} 
\sum_{i \in A_2} \frac{x_i y_i}{\pi_{1i} q_i}.$$ 
%\footnote{
%  \textcolor{blue}{Caleb, we do not have to use $\pi_{2i \mid 1}^{(2)}$ in computing
%  $\hat{\beta}_2$. Please check my book.}
%  \textcolor{red}{Thanks for the check. I
%checked it and I must have gotten $\pi_{1i}$ and $\pi_{2i}$ confused.}}
%\footnote{\textcolor{red}{I was initially thinking of using $\hat \beta_2$ without $q_i$ to be
%  more consistent with how I defined the two-phase regression estimator;
%  however, I see your point about using $q_i$ to connect this estimator with the
%superpopulation model.}}

@@

\begin{theorem}[Design Consistency]
  Under regularity conditions,

  $$\hat Y_{DCE} = \hat Y_\ell(\lambda^*, \phi^*) + o_p(N / n_2)$$

@@

  $$\hat Y_{\ell}(\hat \lambda, \phi^*) = \hat Y_{DCE}(\hat \lambda) + 
  \left(\sum_{i \in A_1} w_{1i} z_i q_i = \sum_{i \in A_2} w_{1i} \hat w_{2i|1}(\hat
  \lambda) z_i q_i\right)\phi^*$$

@@

\begin{proof}
  In this proof, we derive the solution to Equation~\ref{eq:primal} and show
  that it is asymptotically equivalent to a regression estimator. Using the
  method of Lagrange multipliers, to solve Equation~\ref{eq:primal} we need to
  minimize,

@@

  The final equality comes from the fact that 
  $E\left[\frac{\partial}{\partial \lambda}\hat Y_\ell(\lambda^*, \phi^*)\right]
  = 0$, $\frac{\partial}{\partial \lambda^2} \hat w_{2i|1}(\lambda^*)$ is
  bounded and $|\hat \lambda - \lambda^*| = o_p(n_2^{-1/2})$, which proves our
  result.

%\begin{proof}
%  First, we derive the solution for $\hat Y_{DCE}$, and then derive the
%  asymptotic variance of this estimator using the linearization technique of
%  \cite{randles1982asymptotic}.
%
%  We want to solve Equation~\ref{eq:primalloss} subject to the constraints in
%  Equations~\ref{eq:calconst1} and \ref{eq:calconst2}. Using the method of
%  Lagrange multipliers we have a Lagrangian of 
%
%  $$\mathcal{L}(w_2) = -\sum_{i \in A_2} w_{1i} G(w_{2i})q_i + \lambda 
%  \left(\sum_{i \in A_2} w_{1i} w_{2i} z_i - \sum_{i \in A_1} w_{1i} z_i\right).$$
%
%  Our first order conditions yield,
%
%  \begin{align*}
%    0 &= \frac{\partial}{\partial w_{2i}} \mathcal{L}(w_{2}) \\ 
%      &= -w_{1i} g(w_{2i}) q_i + \lambda w_{1i} z_i.
%  \end{align*}
%
%  This means that $\hat w_{2i} = g^{-1}(\hat \lambda z_i / q_i)$ and since $\hat
%  \lambda$ is determined from the solution to Equations~\ref{eq:calconst1} and
%  \ref{eq:calconst2}. Hence, $\hat Y_{DCE} = \sum_{i \in A_2} w_{1i} 
%  \hat w_{2i}(\hat \lambda) y_i$.
%
%  To get the variance of $\hat Y_{DCE}$ we use the linearization technique of
%  \cite{randles1982asymptotic}. First, notice that 
%
%  $$\hat Y_{DCE} = \sum_{i \in A_2} w_{1i} \hat w_{2i}(\hat \lambda) y_i =
%  \sum_{i \in A_2} w_{1i} \hat w_{2i}(\hat \lambda) y_i + \left(
%  \sum_{i \in A_1} w_{1i} z_i -
%  \sum_{i \in A_2} w_{1i} \hat w_{2i}(\hat \lambda) z_i\right)\phi
%  := \hat Y_\ell(\hat \lambda, \phi).$$
%
%  We can find the value of $\phi$ such that $E[\frac{\partial}{\partial
%  \lambda}\hat Y_\ell(\lambda, \phi)]_{\lambda = \lambda^*}$ where $\lambda^*$
%  is the probability limit of $\hat \lambda$. Notice, that 
%  $\lambda^* = (\bf 0, 1)$ because $\hat w_{2i} \to \pi_{2i|1}^{-1}$. This means
%  that the optimal value of $\phi$ solves,
%
%  $$E\left[\frac{\partial}{\partial \lambda} \hat Y_\ell(\lambda, \phi)\right] =
%  E\left[\sum_{i \in A_2} w_{1i} \frac{\partial}{\partial \lambda} w_{2i|1}(\lambda)
%    y_i - \phi \sum_{i \in A_2} w_{1i} z_i \frac{\partial}{\partial \lambda}
%    w_{2i|1}(\lambda) / q_i \right]$$
%
%  which means that
%
%  $$\phi^* = \left[\sum_{i \in U} \pi_{2i|1} \left(\frac{z_i z_i^T}{
%    g'(g^{-1}(g(d_{2i|1}) / q_i))q_i^2}\right)\right]^{-1} \sum_{i \in U} \pi_{2i|1}
%    \left(\frac{z_i y_i}{g'(g^{-1}(g(d_{2i|1}) / q_i)) q_i}\right).$$
%
%  Hence,
%
%  \begin{align*}
%    \hat Y_\ell(\lambda^*, \phi^*) 
%    &= \sum_{i \in A_2} w_{1i} \pi_{2i|1}^{-1}
%    y_i + \left(\sum_{i \in A_1} w_{1i} z_i / q_i -
%      \sum_{i \in A_2} w_{1i} \pi_{2i|1}^{-1} z_i / q_i\right)\phi^* \\ 
%    &= \sum_{i \in A_1} w_{1i} \eta_i
%  \end{align*}
%
%  where 
%
%  $$\eta_i = z_i \phi^* / q_i + \frac{\delta_{2i|1}}{\pi_{2i|1}} \left(y_i
%  - z_i \phi^* / q_i\right).$$
%
%  To analyze the variance, consider the reverse framework of
%  \cite{fay1992inferences}, \cite{kim2006replication}, and \cite{shao1999variance}.
%  In this setup, we assume that $\mathcal{R} = \{\delta_{2i|1}\}_{i \in U}$ is
%  known at the
%  finite population level. Then with this we have,
%
%  \begin{align*}
%    V(\hat Y_{\ell}(\lambda^*, \phi^*)) 
%    &= V\left(\sum_{i \in A_1} w_{1i} \eta_i(\phi^*)\right) \\
%    &= V\left(E\left[\sum_{i \in A_1} w_{1i}\eta_i(\phi^*)\mid\mathcal{R}\right]\right) 
%    +E\left[V\left(\sum_{i \in A_1} w_{1i} \eta_i(\phi^*)\mid\mathcal{R}\right)\right]\\
%    &= V\left(\sum_{i \in U} \eta_i(\phi^*)\right) + E\left[\sum_{i \in U} 
%    \sum_{j \in U} \Cov(\delta_{1i}, \delta_{1j}) 
%    w_{1i} w_{1j} \eta_i(\phi^*) \eta_j(\phi^*)\right]\\
%  \end{align*}
%
%  We can estimate this variance using 
%
%  $$\hat V_{DCE} = \sum_{i \in A_1} \sum_{j \in A_1} \left(\frac{\pi_{1ij} -
%  \pi_{1i}\pi_{1j}}{\pi_{1ij}}
%    w_{1i} w_{1j} \hat \eta_i \hat \eta_j \right)
%  $$
%
%  for $\hat \eta_i = z_i \hat \phi / q_i + \frac{\delta_{2i|1}}{\pi_{2i|1}} \left(y_i
%  - z_i \hat \phi / q_i\right)$ where 
%
%  $$\hat \phi = \left[\sum_{i \in A_2} w_{1i}\left(\frac{z_i z_i^T}{
%  g'(g^{-1}(g(d_{2i|1}) / q_i))q_i^2}\right)\right]^{-1} \sum_{i \in A_2} w_{1i}
%    \left(\frac{z_i y_i}{g'(g^{-1}(g(d_{2i|1}) / q_i)) q_i}\right).$$
%
%  The problem with this estimator is that it is biased as $E[\hat V_{DCE}]$ is
%  asymptotically equivalent to
%  $V\left(\sum_{i \in A_1} w_{1i} \eta(\phi^*)\right)$. This yields a bias of 
%
%  \begin{align*}
%    \text{Bias}(\hat V_{DCE}) 
%    &= V\left(\sum_{i \in U} \eta_i(\phi^*)\right)\\ 
%    &= \sum_{i \in U} \sum_{j \in U} \Delta_{2ij|1} w_{2i|1}
%    w_{2j|1} (y_i - z_i \phi^* / q_i)(y_j - z_j \phi^* / q_j).
%  \end{align*}
%
%  where $\Delta_{2ij|1} = \pi_{2ij|1} - \pi_{2i|1} \pi_{2j|1}$. 
%  However, we can estimate this bias with
%
%  $$\widehat{\text{Bias}}(\hat V_{DCE}) = 
%  \sum_{i \in A_2} \sum_{j \in A_2} w_{1ij} w_{2ij|1} w_{2i|1} w_{2j|1} 
%  \Delta_{2ij|1} (y_i - z_i \phi^* / q_i)(y_j - z_j \phi^* / q_j).$$
%
%\end{proof}

@@

where $\Phi_3$ is the CDF of a t-distribution with 3 degrees of freedom.
This is a two-phase extension of the setup in \cite{kwon2024debiased}. We
consider a finite population of size $N = 10,000$ with both the Phase 1 and
Phase 2 sampling occuring under Poisson (Bernoulli) sampling. This yields a
Phase 1 sample
size of $E[n_1] \approx 1100$ and a Phase 2 sample size of
$E[n_2] \approx 550$. In the Phase 1 sample, we observe 
$(X_1, X_2)$ while in the Phase 2 sample we observe $(X_1, X_2, Y)$. This
simulation does not deal with model misspecification, and we compare the
proposed method for the parameter $\bar Y_N$ with four approaches:

@@

\textcolor{blue}{
( Materials in Section 11.4 can be used here. I have copy-and-pasted the
textbook materials below. Please modify them.  )
}
\textcolor{red}{I will do this shortly.}

@@

where $\pi_{1i}$ is the probability of $i \in A_1$ and $\pi_{2i} = \Pr(i \in
A_2)$. \textcolor{red}{I don't know if it makes sense to change the Phase 2
selection probability as $\pi_{2i|1}$. Should I keep it at $\pi_{2i}$? But if
I do, how is the two phase setup useful?} We can combine these estimates to get
$\hat X_c = W \hat X_1 + (1 - W)\hat X_2$ for some matrix $W$ (see
\cite{merkouris2004combining} for the optimal choice of $W$). We can then define
a regression estimator as

@@

@@

>>>>

where for $q_i = q(x_i)$ and is a function of $x_i$,
$$
\hat \beta_q = \left(\sum_{i \in A_2} 
  \frac{x_i x_i'}{\pi_{1i} q_i}\right)^{-1} 
\sum_{i \in A_2} \frac{x_i y_i}{\pi_{1i} q_i}.$$

@@

\begin{theorem}[Design Consistency]\label{thm:dc1}
  Under some regularity conditions,

  $$\hat Y_{DCE} = \hat Y_\ell(\lambda^*, \phi^*) + O_p(N / n_2)$$

@@

  $$\hat Y_{\ell}(\hat \lambda, \phi^*) = \hat Y_{DCE}(\hat \lambda) + 
  \left(\sum_{i \in A_1} w_{1i} z_i q_i - \sum_{i \in A_2} w_{1i} \hat w_{2i|1}(\hat
  \lambda) z_i q_i\right)\phi^*$$

@@

   \begin{eqnarray*}
   \hat Y_{\ell}( \lambda^*, \phi^*) &=&   \hat{Y}_{\pi^*} + 
  \left(\sum_{i \in A_1} w_{1i} x_i  -  \sum_{i \in A_2} w_{1i} \pi_{2i \mid
  1}^{-1} x_i  \right)^T \phi_1^* + \left(\sum_{i \in A_1} w_{1i} g_i   -
\sum_{i \in A_2} w_{1i} \pi_{2i \mid 1}^{-1}g_i  \right)^T \phi_2^*  
  \end{eqnarray*} 
  and  $$\begin{pmatrix}
  \phi_1^* \\
  \phi_2^* 
  \end{pmatrix}
  = \left[ \sum_{i \in U} \frac{\pi_{2i \mid 1} }{ g'(d_{2i|1}) q_i} 
  \begin{pmatrix}
  \bx_i \bx_i^T &   \bx_i g_i   \\
  g_i  \bx_i^T   & g_i^2     \end{pmatrix} \right]^{-1}
  \sum_{i \in U} \frac{\pi_{2i|1}}{ g'(d_{2i | 1}) q_i} \begin{pmatrix}
    \bx_i \\ g_i 
  \end{pmatrix}y_i $$
with $g_i = g( \pi_{2i |1}^{-1}) q_i$.
\end{theorem}

\textcolor{red}{I have tried to improve the expression of the linearization
formula. Please check if my algebra above is correct. }
\textcolor{blue}{This is correct. I have almost the same expression in
Theorem~\ref{thm:dc2}.}
\begin{proof}
  In this proof, we derive the solution to Equation~\ref{eq:primal} and show
  that it is asymptotically equivalent to a regression estimator. Using the
  method of Lagrange multipliers, to solve Equation~\ref{eq:primal} we need to
  minimize,

@@

  The final equality comes from the fact that 
  $E\left[\frac{\partial}{\partial \lambda}\hat Y_\ell(\lambda^*, \phi^*)\right]
  = 0$, $\frac{\partial}{\partial \lambda^2} \hat w_{2i|1}(\lambda^*)$ is
  bounded and $|\hat \lambda - \lambda^*| = O_p(n_2^{-1/2})$, which proves our
  result.
\end{proof}

@@

where $\Phi_3$ is the CDF of a t-distribution with 3 degrees of freedom.

\textcolor{red}{The simulation setup is somewhat strange. The first order inclusion probability for the second-phase sampling, $\pi_{2i \mid 1}$, is a function of $x_{4i}$ which is completely independent of $(x_{1i}, x_{2i}, y_i)$. In this case, your second-phase sampling is essentially equivalent to the simple random sampling. }
This is a two-phase extension of the setup in \cite{kwon2024debiased}. We
consider a finite population of size $N = 10,000$ with both the Phase 1 and
Phase 2 sampling occuring under Poisson (Bernoulli) sampling. This yields a
Phase 1 sample
size of $E[n_1] \approx 1100$ and a Phase 2 sample size of
$E[n_2] \approx 550$. In the Phase 1 sample, we observe 
$(X_1, X_2)$ while in the Phase 2 sample we observe $(X_1, X_2, Y)$. This
simulation does not deal with model misspecification, and we compare the
proposed method for the parameter $\bar Y_N$ with four approaches:

@@

@@

where $\pi_{1i}$ is the probability of $i \in A_1$ and $\pi_{2i} = \Pr(i \in
A_2)$. \textcolor{red}{I don't know if it makes sense to change the Phase 2
selection probability as $\pi_{2i|1}$. Should I keep it at $\pi_{2i}$? But if
I do, how is the two phase setup useful?} We can combine these estimates to get
$\hat X_c = W \hat X_1 + (1 - W)\hat X_2$ for some matrix $W$ (see
\cite{merkouris2004combining} for the optimal choice of $W$), and can then define
a regression estimator as

@@

The methodology for the non-nested two phase sample is very similar to the setup
described as part of Topic 1. Given a strictly convex differentiable function,
$G: \mathcal{V} \to \mathbb{R}$, the goal is to solve

\begin{equation}\label{eq:nnopt}
\hat w_2 = \argmin_w \sum_{i \in A_2} G(w_{2i}) q_i \text{ such that } 
\sum_{i \in A_2} w_{2i} x_i = \hat X_{GLS} \text{ and } 
\sum_{i \in A_2} w_{2i} g(d_{2i}) q_i = \sum_{i \in U} g(d_{2i}) q_i
\end{equation}

for $g(x) = G'(x)$ and a known choice of $q_i \in \mathbb{R}$. The difference
between solving Equation~\ref{eq:nnopt} and Equation~\ref{eq:primal} is that the
estimator $\hat X_{GLS}$ is estimated using GLS from other sample(s). Before using
$\hat X_{GLS}$ in the debiased calibration estimator, we need to estimate it
from the non-nested samples.

We can get multiple estimates of $\hat X$,

$$\hat X_1 = \sum_{i \in A_1} \frac{x_i}{\pi_{1i}} \text{ and }
\hat X_2 = \sum_{i \in A_2} \frac{x_i}{\pi_{2i}}.$$

Let $V_1$ and $V_2$ be known variance matrices for $\hat X_1$ and $\hat X_2$,
then the optimal combined GLS estimates is

$$\hat X_c = \frac{V_1^{-1} \hat X_1 + V_2^{-1} \hat X_2}{V_1^{-1} + V_2^{-1}}.$$

We can constuct a non-nested two phase estimator $\hat Y_{NNE}$ for $Y_N$ where
$\hat Y_{NNE} = \sum_{i \in A_2} \hat w_{2i} y_i$ and $\hat w_{2i}$ solves
Equation~\ref{eq:nnopt}.

@@

\begin{theorem}[Design Consistency]\label{thm:dc2}
  Under some regularity conditions, $\hat Y_{NNE} = \hat Y_{\ell, NNE}(\lambda^*,
  \phi^*) + O_p(Nn_2^{-1})$ where

  $$\hat Y_{\ell, NNE}(\lambda^*, \phi^*) = \sum_{i \in A_2} \hat w_{2i}(
  \lambda^*) + \left(T - \sum_{i \in A_2} \hat w_{2i}(\lambda^*) z_i q_i\right)
  \phi^*$$

  and 
  $$\phi^* =
  \left(\sum_{i \in U} \frac{\pi_{2i} q_i}{g'(d_{2i})} 
  \begin{bmatrix}
    x_i^2 / q_i & x_i g(d_{2i}) / q_i \\
    x_i g(d_{2i}) / q_i & g(d_{2i})^2
  \end{bmatrix}
  \right)^{-1}
  \sum_{i \in U} \frac{\pi_{2i} y_i}{g'(d_{2i})} 
  \begin{bmatrix} x_i / q_i \\ g(d_i) \end{bmatrix}.
  $$

\begin{proof}
  The proof of this result is very similar to the proof the Theorem~\ref{thm:dc1}.
  The biggest difference is that the total for $X$ is estimated from both samples
  using $\hat X_c$ instead of $\hat X_{HT}$ from the Phase 1 sample.

  Since $\hat Y_{NNE} = \sum_{i \in A_2} \hat w_{2i}(\hat \lambda)y_i$ where
  $\hat \lambda$ solves

  \begin{equation}
    \sum_{i \in A_2} \hat w_{2i}(\lambda) q_i
    \underbrace{
    \begin{bmatrix} 
      x_i / q_i \\ g(d_i)
  \end{bmatrix}}_{z_i} =
  \underbrace{\begin{bmatrix} 
      \hat X_c \\
      \sum_{i \in U} g(d_i) q_i
  \end{bmatrix}}_{T}
  \end{equation}

  we have

  $$\hat Y_{\ell, NNE} (\hat \lambda, \phi) = \sum_{i \in A_2} \hat w_{2i}(\hat
  \lambda) + \left(T - \sum_{i \in A_2} \hat w_{2i}(\hat \lambda) z_i q_i\right)
  \phi.$$

  If we choose $\phi^*$ such that $E\left[\frac{\partial}{\partial \lambda} 
    \hat Y_{\ell, NNE}(\lambda^*, \phi^*)\right] = 0$, then

  $$\phi^* =
  \begin{bmatrix}
    \phi^*_1 \\ \phi^*_2
  \end{bmatrix} = 
  \left(\sum_{i \in U} \frac{\pi_{2i} q_i}{g'(d_{2i})} 
  \begin{bmatrix}
    x_i^2 / q_i & x_i g(d_{2i}) / q_i \\
    x_i g(d_{2i}) / q_i & g(d_{2i})^2
  \end{bmatrix}
  \right)^{-1}
  \sum_{i \in U} \frac{\pi_{2i} y_i}{g'(d_{2i})} 
  \begin{bmatrix} x_i / q_i \\ g(d_i) \end{bmatrix}.
  $$

  Hence, by a Taylor expansion around $\hat \lambda$,

  $$\hat Y_{NNE}(\hat \lambda) = \hat Y_{\ell, NNE}(\lambda^*, \phi^*) +
  O_p(Nn_2^{-1}).$$

\begin{theorem}[Variance Estimation]
  The variance of $\hat Y_{NNE}$ is

  \begin{align*}
    \Var(\hat Y_{NNE}(\hat \lambda)
    &= (\phi_1^*)^T \Var(\hat X_c) \phi_1^* + 
    \sum_{i \in U} \sum_{j \in U} \frac{\Delta_{2ij}}{\pi_{2i}\pi_{2j}} (y_i - z_i \phi^* q_i)(y_j - z_j \phi^* q_j)\\
    &\qquad + (1 - W)\phi_1^* \sum_{i \in U} \sum_{j \in U} \Delta_{2ij} \frac{x_i}{\pi_{2i}}
    \frac{(y_j - z_j \phi^*_1 q_j)}{\pi_{2j}}\\
  \end{align*}

  We can estimate the variance using

  \begin{align*}
    \hat V_{NNE} 
    &= (\hat \phi_1)^T \Var(\hat X_c) \hat \phi_1 + 
    \sum_{i \in A_2} \sum_{j \in A_2} \frac{\Delta_{2ij}}{\pi_{2ij}\pi_{2i}\pi_{2j}} 
    (y_i - z_i \hat \phi q_i)(y_j - z_j \hat \phi q_j) \\
    &\qquad + (1 - W)\hat \phi_1 \sum_{i \in A_2} \sum_{j \in A_2} \frac{\Delta_{2ij}}{\pi_{2ij}}
    \frac{x_i}{\pi_{2i}} \frac{(y_j - z_j \hat \phi_1 q_j)}{\pi_{2j}}
  \end{align*}

  $$\hat \phi =
  \begin{bmatrix}
    \hat \phi_1 \\ \hat \phi_2
  \end{bmatrix} = 
  \left(\sum_{i \in A_2} \frac{q_i}{g'(d_{2i})} 
  \begin{bmatrix}
    x_i^2 / q_i & x_i g(d_{2i}) / q_i \\
    x_i g(d_{2i}) / q_i & g(d_{2i})^2
  \end{bmatrix}
  \right)^{-1}
  \sum_{i \in A_2} \frac{y_i}{g'(d_{2i})} 
  \begin{bmatrix} x_i / q_i \\ g(d_i) \end{bmatrix}.
  $$
\end{theorem}

\begin{proof}
  From Theorem~\ref{thm:dc2}, we know that $\hat Y_{NNE}(\hat \lambda) = 
  \hat Y_{\ell, NNE}(\lambda^*, \phi^*) + O_p(Nn_2^{-1})$. Hence, the variance
  of $\hat Y_{NNE}(\hat \lambda)$ is

  \begin{align*}
    \Var(\hat Y_{NNE}(\hat \lambda)) 
    &= \Var(\hat Y_{\ell, NNE}(\lambda^*, \phi^*) + O_p(Nn_2^{-1})) \\ 
    &= \Var\left(\sum_{i \in A_2} \hat w_{2i}(\lambda^*) y_i + \left(T - \sum_{i
    \in A_2} \hat w_{2i}(\lambda^*) z_i q_i\right)\phi^*\right)\\
    &= (\phi_1^*)^T \Var(\hat X_c) \phi_1^* + 
    \sum_{i \in U} \sum_{j \in U} \frac{\Delta_{2ij}}{\pi_{2i}\pi_{2j}} (y_i - z_i \phi^* q_i)(y_j - z_j \phi^* q_j)\\
    &\qquad+ 2 \Cov\left(\hat X_c \phi_1^*, \sum_{i \in A_2} \frac{(y_i - z_i \phi^*
    q_i)}{\pi_{2i}}\right) \\
    &= (\phi_1^*)^T \Var(\hat X_c) \phi_1^* + 
    \sum_{i \in U} \sum_{j \in U} \frac{\Delta_{2ij}}{\pi_{2i}\pi_{2j}} (y_i - z_i \phi^* q_i)(y_j - z_j \phi^* q_j)\\
    &\qquad + (1 - W)\phi_1^* \sum_{i \in U} \sum_{j \in U} \Delta_{2ij} \frac{x_i}{\pi_{2i}}
    \frac{(y_j - z_j \phi^*_1 q_j)}{\pi_{2j}}\\
  \end{align*}

  where the last equality comes from the fact that $\hat X_c = W\hat X_1 + (1 -
  W) \hat X_2$. To have an unbiased estimator of the variance we can use:

  \begin{align*}
    \hat V_{NNE} 
    &= (\hat \phi_1)^T \Var(\hat X_c) \hat \phi_1 + 
    \sum_{i \in A_2} \sum_{j \in A_2} \frac{\Delta_{2ij}}{\pi_{2ij}\pi_{2i}\pi_{2j}} 
    (y_i - z_i \hat \phi q_i)(y_j - z_j \hat \phi q_j) \\
    &\qquad + (1 - W)\hat \phi_1 \sum_{i \in A_2} \sum_{j \in A_2} \frac{\Delta_{2ij}}{\pi_{2ij}}
    \frac{x_i}{\pi_{2i}} \frac{(y_j - z_j \hat \phi_1 q_j)}{\pi_{2j}}
  \end{align*}

  $$\hat \phi =
  \begin{bmatrix}
    \hat \phi_1 \\ \hat \phi_2
  \end{bmatrix} = 
  \left(\sum_{i \in A_2} \frac{q_i}{g'(d_{2i})} 
  \begin{bmatrix}
    x_i^2 / q_i & x_i g(d_{2i}) / q_i \\
    x_i g(d_{2i}) / q_i & g(d_{2i})^2
  \end{bmatrix}
  \right)^{-1}
  \sum_{i \in A_2} \frac{y_i}{g'(d_{2i})} 
  \begin{bmatrix} x_i / q_i \\ g(d_i) \end{bmatrix}.
  $$
